Supporting Information

### 2018-04-20 SupportingInformation.Rmd
ylim NA plot fixed

Plotter_Cause4copula_GOF(fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=13,method="spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=4,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=13,method="kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=4,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
# I need to fix that SG_kendall ylimit error
#----------------------------
#pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=12, height=6)
#op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

#Plotter_Cause4copula_GOF(fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(fcode=13,method="spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(fcode=14,method="spearman",num_keep_last=2500,BS=1000)

#Plotter_Cause4copula_GOF(fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(fcode=13,method="kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(fcode=14,method="kendall",num_keep_last=2500,BS=1000)

#op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
#plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
#legend("top", c("noise","population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
#       cex = 1.5, pch = c(2, 6, 16, 16), lty = c(1, 1, NA, NA), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
#       bty = "n") 
#par(op)
#dev.off()
```

@@

```{r cause4copula_stat_C_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=3,method="spearman",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_C_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=3,method="spearman",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_SC_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=13,method="spearman",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_SC_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=13,method="kendall",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_G_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=4,method="spearman",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_G_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=4,method="kendall",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_SG_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=14,method="spearman",lb=0,ub=0.1)
dev.off()
```

@@

```{r cause4copula_stat_SG_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=14,method="kendall",lb=0,ub=0.1)
dev.off()
```

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last **500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf)

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last **2500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Clayton** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_C_spear}](./Results/Cause4copula_results/Clayton_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Clayton** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_C_kend}](./Results/Cause4copula_results/Clayton_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Clayton** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SC_spear}](./Results/Cause4copula_results/SClayton_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Clayton** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SC_kend}](./Results/Cause4copula_results/SClayton_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Gumbel** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_G_spear}](./Results/Cause4copula_results/Gumbel_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Gumbel** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_G_kend}](./Results/Cause4copula_results/Gumbel_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Gumbel** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SG_spear}](./Results/Cause4copula_results/SGumbel_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Gumbel** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SG_kend}](./Results/Cause4copula_results/SGumbel_kendall.pdf)

>>>>

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=10000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=10000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

@@

```{r cause4copula_stat_C_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_C_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SC_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SC_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_G_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=4,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_G_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=4,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SG_spear, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=14,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

@@

```{r cause4copula_stat_SG_kend, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed=101)
#----------------------
pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=10000,numsim=50,fcode=14,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 10000 points are generated but we kept last **500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf)

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 10000 points are generated but we kept last **2500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Clayton** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_C_spear}](./Results/Cause4copula_results/Clayton_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Clayton** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_C_kend}](./Results/Cause4copula_results/Clayton_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Clayton** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SC_spear}](./Results/Cause4copula_results/SClayton_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Clayton** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SC_kend}](./Results/Cause4copula_results/SClayton_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Gumbel** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_G_spear}](./Results/Cause4copula_results/Gumbel_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Gumbel** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_G_kend}](./Results/Cause4copula_results/Gumbel_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Gumbel** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SG_spear}](./Results/Cause4copula_results/SGumbel_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Gumbel** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 10000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SG_kend}](./Results/Cause4copula_results/SGumbel_kendall.pdf)
